Notes on the low density parameters in {\tt MAESTRO}

### 2009-02-06 docs/lo_density/lo_density.tex
split out the content
switch over to book format for the master document -- this makes the sectioning more natural
minor updates to anelastic cutoff section

\documentclass[11pt]{article}

\tolerance=600

\usepackage{amsmath,color}

% Margins
\usepackage[lmargin=0.5in,rmargin=0.5in,tmargin=0.75in,bmargin=0.75in]{geometry}

\def\half  {\frac{1}{2}}
\def\dt    {\Delta t}
\def\kth   {k_{\rm th}}

\def\edge  {\rm EDGE}
\def\mac   {\rm MAC}
\def\trans {\rm TRANS}

\def\eb    {{\bf e}}
\def\fb    {{\bf f}}
\def\ib    {{\bf i}}
\def\Ub    {{\bf U}}

\def\Ubt   {\widetilde{\bf U}}
\def\ut    {\tilde{u}}
\def\vt    {\tilde{v}}
\def\wt    {\tilde{w}}

\title{Notes on the low density parameters in {\tt MAESTRO}}

\setlength{\marginparwidth}{0.75in}
\newcommand{\MarginPar}[1]{\marginpar{%
\vskip-\baselineskip %raise the marginpar a bit
\raggedright\tiny\sffamily
\hrule\smallskip{\color{red}#1}\par\smallskip\hrule}}

\begin{document}

\maketitle
\tableofcontents

@@

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt
  delta\_gamma1} to zero for $r\in[{\tt anelastic\_cutoff\_coord},{\tt
    r\_end\_coord}]$.
\end{itemize}

>>>>

@@

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r\in[{\tt anelastic\_cutoff\_coord},{\tt r\_end\_coord}]$.

\item In {\tt sponge}, {\tt anelastic\_cutoff} is used in a problem
  dependent way.

\item In {\tt probin}, {\tt anelastic\_cutoff} is set to $3\times 10^6$
  by default.

\end{itemize}
